Proof by reflection for equalities in algebraic structures

### 2014-06-11 newPaper/paper.tex
added one file

\conferenceinfo{PLPV ’14, Co-located with POPL 2014}{January 21, 2014, San Diego, CA, USA.}
\copyrightyear{2013} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\preprintfooter{Our paper for PLPV’14}
\doi{nnnnnnn.nnnnnnn}

@@

\authorinfo{Edwin Brady\and Franck Slama}
           {University of St Andrews, United-Kingdom}
           {ecb10@st-andrews.ac.uk \and fs39@st-andrews.ac.uk}
\bibliographystyle{abbrvnat}

@@

@@

\input{./content/idrisOverview}

\input{./content/method}

-> Présenter type class

-> Présenter type de donnée (sans index pour la valeur)

-> Expliquer qu'on peut paramétrer le type pour capturer la valeur effective representee

\section{Datatypes}

Lots of text.

\subsection{Hierarchy of algebraic theorys}

Lots of text.

The exemple with Nat is a monoid

More text.

\subsection{Reflection in an abstract syntax}

Lots of text.

More text.

>>>>

\conferenceinfo{POPL ’15}{January 15-17, 2015, Mumbai, India.}
\copyrightyear{2014} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\preprintfooter{Our paper for POPL '15}
\doi{nnnnnnn.nnnnnnn}

@@

%\authorinfo{Edwin Brady\and Franck Slama}
%           {University of St Andrews, United-Kingdom}
%           {ecb10@st-andrews.ac.uk \and fs39@st-andrews.ac.uk}
\authorinfo{Author's name omitted for submission}
           {University of ..., Country}
           {email address omitted for submission}

\bibliographystyle{abbrvnat}

@@

Plan : \\
- Intro (1 page): problem + contribution : NOT SPECIFIC ENOUGH YET. TOO GENERAL, TOO BORING. HOW TO CAPTURE THE INTEREST ? \\
- The problem on a simplified idea (2 pages) : Assoc : that will present the reflection and correct by construction sides on a little example in order to build the intuition.  \\
- The idea (2 pages)  : the different typeclass AND reflected data types AND functions decideEq \\
- The details (4/5 pages): Normalizations functions in Magma, Semi-Group, monoid, Group \\ 
- (1/2 pages) : Coating and automatic metaification \\
- Related work (1 page): We may be slower (I'll have to check), but this is NICER. The proof of correctness of the  implementation of the normalization is trivial to obtain (and this is what we want to get !) \\
- Conclusion (1 page)

@@
